\documentclass[10pt]{article}

%A Few Useful Packages
\RequirePackage{color, graphicx}
\usepackage{parskip, titlesec, verbatim}

%For setting page
\usepackage{geometry}
\geometry{a4paper, left = 14mm, right = 14mm, top = 13mm, bottom = 13mm}

%For changing font
\usepackage[T1]{fontenc}
\usepackage[defaultsans]{droidsans}
\renewcommand*\familydefault{\sfdefault}

%For hyperlinks
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0, 0.2, 0.6}
\hypersetup{colorlinks, breaklinks, urlcolor = linkcolour, linkcolor = linkcolour}

%For section titles
\titlespacing{\section}{0pt}{0pt}{0pt}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]

\begin{document}

\pagestyle{empty}

\begin{center}
	\begin{tabular}{l r}
		{\Huge \textsc{\textbf{Berk Erol}}} & {\Large \textsc{Computer Engineer}}
	\end{tabular}

	\section{\textcolor[RGB]{200, 0, 0}{\textbf{Personal Info}}}
	\begin{tabular}{l l}
		\textbf{Address:} Kadikoy, Istanbul, Turkey                               & \textbf{Phone:} +90 545 852 52 77                                          \\
		\textbf{Email:} \href{mailto:berk.erol@boun.edu.tr}{berk.erol@boun.edu.tr} & \textbf{Website:} \href{https://berkerol.github.io}{berkerol.github.io}    \\
		\textbf{GitHub:} \href{https://github.com/berkerol}{berkerol}              & \textbf{LinkedIn:} \href{https://www.linkedin.com/in/berk-erol}{Berk Erol} \\
		\textbf{Passport:} Valid until 2020                                       & \textbf{Driver License:} Category B
	\end{tabular}
\end{center}

\section{\textcolor[RGB]{0, 100, 200}{\textbf{Education}}}
\begin{tabular}{r | l}
	2018 & Erasmus Program in Informatics, Technical University of Munich, Munich, Germany
	\\\multicolumn{2}{c}{}
	\\Expected June 2019 & B.S. in Computer Engineering, Bogazici University, Bebek, Istanbul, Turkey
	\\2014 & Current GPA: 3.12/4.00
	\\\multicolumn{2}{c}{}
	\\2014 & Cagaloglu Anadolu Lisesi, Fatih, Istanbul, Turkey
	\\2009 & GPA: 4.46/5.00
\end{tabular}

\section{\textcolor[RGB]{100, 0, 200}{\textbf{Experience}}}
\begin{tabular}{r | p{15cm}}
	Now - May 2017 & \textbf{Student Ambassador in IBM, Istanbul, Turkey}
	\\\multicolumn{2}{c}{}
	\\August 2017 & \textbf{Software Engineering Intern in OBSS, Istanbul, Turkey}
	\\July 2017 & Developing an advanced website from scratch about job advertisements for both applicants and HR specialists. Uses modern services such as LDAP \& LinkedIn authentication, Solr.
	\\\multicolumn{2}{c}{}
	\\June 2017 & \textbf{Software Engineering Intern in Khan Academy, STFA Construction Group, Istanbul, Turkey}
	\\ & Improving and maintaining the overall website. Fixing bugs, optimizing website performance, adding new features (some front-end elements and URL Rewrite).
	\\\multicolumn{2}{c}{}
	\\January 2016 & \textbf{Student Assistant in Computer Engineering Dep., Bogazici University, Istanbul, Turkey}
	\\October 2015 & Teaching freshmen algorithms, data structures, sorting and searching in C.
\end{tabular}

\section{\textcolor[RGB]{0, 180, 120}{\textbf{Skills and Interests}}}
\begin{itemize}
	\item \textbf{Languages:} Turkish (Native), English (Proficient), German (Fluent, C1 level of DSD II Certificate)
	\item \textbf{Fluent in:} C/C++/C\# \& Java \& Python and object-oriented programming
	\item \textbf{Web Technologies:} HTML5, CSS3, JavaScript, ES6, jQuery, Bootstrap, ASP, PHP, Spring, SQL, Solr, LDAP
	\item \textbf{Knowledge of:} Android, Prolog, Scheme, Smalltalk, MATLAB, Wolfram, Verilog, Assembly, \LaTeX, Unix, Git, AWS
	\item \textbf{Interests:} Alternative energies, artificial intelligence, cryptography, graphic design, open source, virtual reality
\end{itemize}

\section{\textcolor[RGB]{200, 100, 0}{\textbf{Activities, Societies and Trainings}}}
\begin{itemize}
	\item \textbf{Open source projects on GitHub: }
	      Software designed by myself, CV \& Website source code, school projects.
	\item \textbf{CoderDojo Mentor at COMPEC, Bogazici University (March 2017 - April 2017)}
	      \\Voluntary work for helping children create basic games using the MIT's Scratch Tool.
	\item \textbf{Member of VRFirst BAU, Bahcesehir University (Since April 2016): }
	      Attending meetings, seminars, trainings and learning about new technologies and ongoing projects in the virtual reality lab.
	\item \textbf{BIC Angels Startnowhow, Bogazici University (September 2015 - June 2016): }
	      Courses about entrepreneurship and startups with guest speakers talking about the experiences and hardships of a startup.
	\item \textbf{Headguide at Sports Fest, Bogazici University (May 2015): }
	      Helping sportsmen all around the world during their stay and organizing events at Sports Fest which is the Turkey's biggest student-organized sports festival.
	\item \textbf{Member of BUNIS - Bogazici University Network of International Students \& ESN - European Student Network (2014 - 2015): }
	      Helping international students and organizing events for them.
	\item \textbf{Member of COMPEC - Bogazici University Computer Eng. Club (2014 - 2016), BÜYAK - Bogazici University Operations Research Club \& ESTIEM - European Students of Industrial Eng. and Management (2014)}
	      \\Contacting companies; networking with business people; organizing and attending trainings, seminars, trips.
	\item \textbf{Java and Android Training, Bogazici University (October 2014 - December 2014)}
	      \\Intense courses from the basics of the Java to a complete Android application with certificate.
\end{itemize}

\begin{comment}
\item \textbf{Social Innovation and Entrepreneurship Seminar, Bogazici University (Oct. 2015)}
\\Seminar by Bogazici University Technology Transfer Office and Young Guru Academy with certificate.
\item \textbf{P\&G Finance Training, Bogazici University (November 2014)}
\\Seminar about financial leadership in product launches with certificate.
\item \textbf{Bogazici Marka Zirvesi, Bogazici University (November 2014)}
\\Intense 2-day branding and marketing seminar series with the participation of managers with certificate.
\end{comment}

\end{document}
